DATA 621 Homework #4

### 2019-11-06 hw4/HW4.Rmd
Added some color to the visualizations

hw4_plot <- function(df, var, strip_dollar_signs = FALSE){
  if(strip_dollar_signs){
    df$X <- strip_dollars(df[[var]])
  } else {
    df$X <- df[[var]]
  }
  plot_1 <- ggplot(df, aes(X, TARGET_FLAG, color = TARGET_FLAG)) +
    geom_jitter() +
    theme_minimal() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.title.y = element_blank())

  plot_2 <- ggplot(df, aes(X, TARGET_AMT, color = TARGET_FLAG)) +
    geom_point() +
    theme_minimal() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.title.y = element_blank())

@@

hw4_categorical_plot <- function(df, var, strip_dollar_signs = FALSE){
  if(strip_dollar_signs){
    df$X <- strip_dollars(df[[var]])
  } else {
    df$X <- df[[var]]
  }
  plot_1 <- ggplot(df, aes(X, TARGET_FLAG, color = TARGET_FLAG)) +
    geom_jitter() +
    theme_minimal() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.title.y = element_blank())

  plot_2 <- df %>%
    filter(TARGET_FLAG == 1) %>%
    ggplot(., aes(X, TARGET_AMT)) +
      geom_boxplot() +
      theme_minimal() +
      theme(legend.position = "none",
            axis.title.x = element_blank(),
            axis.title.y = element_blank())

@@

>>>>

hw4_plot <- function(df, var, strip_dollar_signs = FALSE){
  if(strip_dollar_signs){
    df$X <- strip_dollars(df[[var]])
  } else {
    df$X <- df[[var]]
  }
  plot_1 <- ggplot(df, aes(X, TARGET_FLAG, color = TARGET_FLAG)) +
    geom_jitter() +
    scale_color_brewer(palette="Set1") +
    theme_minimal() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.title.y = element_blank())

  plot_2 <- ggplot(df, aes(X, TARGET_AMT, color = TARGET_FLAG)) +
    geom_point() +
    scale_color_brewer(palette="Set1") +
    theme_minimal() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.title.y = element_blank())

@@

hw4_categorical_plot <- function(df, var, strip_dollar_signs = FALSE){
  if(strip_dollar_signs){
    df$X <- strip_dollars(df[[var]])
  } else {
    df$X <- as.factor(as.character(df[[var]]))
  }
  plot_1 <- ggplot(df, aes(X, TARGET_FLAG, color = TARGET_FLAG)) +
    geom_jitter() +
    scale_color_brewer(palette="Set1") +
    theme_minimal() +
    theme(legend.position = "none",
          axis.title.x = element_blank(),
          axis.title.y = element_blank())

  plot_2 <- df %>%
    filter(TARGET_FLAG == 1) %>%
    ggplot(., aes(X, TARGET_AMT, color = X)) +
      geom_boxplot() +
      scale_color_brewer(palette="Dark2") + #Paired
      theme_minimal() +
      theme(legend.position = "none",
            axis.title.x = element_blank(),
            axis.title.y = element_blank())

@@

### CAR_USE

**Theoretical Effect**
Commercian vehicles are driven more, so might increase probability of collision.

```{r} 
hw4_categorical_plot(df, "CAR_USE")
```

**Observed Effect**
The plot suggests that the use does not increase or decrease the probability of being in an accident or the amount of the claim.

### CLM_FREQ

**Theoretical Effect**
The more claims you filed in the past, the more you are likely to file in the future.

```{r} 
hw4_categorical_plot(df, "CLM_FREQ")
```

**Observed Effect**
Looks like there are few people who signed up for the frequent accident club.  All jokes aside, the theoretical effect is not observed in the data.

### EDUCATION

**Theoretical Effect**
Unknown effect, but in theory more educated people tend to drive more safely
```{r} 
hw4_categorical_plot(df, "EDUCATION")
```

**Observed Effect**
The theoretical effect has no basis and is somewhat elitist.
